Comparing R packages for calculation of persistent homology

### 2020-03-19 tdabench-paper/tdabench.Rmd
fixed misspelling
fixed phrasing

Figure \ref{fig:fin} shows that at high point cloud sizes, GUDHI’s alpha complex outperforms Ripser. 
Theoretically, alpha complexes gain polynomial complexity as the number of points increases whereas Vietoris-Rips complexes gain exponentially \citep{roadmap}.
Specifically, alpha complexes are $O(n^{d/2})$ and Vietoris-Rips complexes are $O(2^n)$ where $n$ is the number of points on a point cloud and $d$ is the dimensions on the point cloud. 
For the conditions in our paper, Vietoris-Rips and alpha complexes both performed better than their theoritical maximums. 
Vietoris-Rips complex calculations consistently had a polynomial growth for both runtime and boundary matrix size while alpha complexes had linear growth.

@@

Based on this theoretical complexity and our results, alpha complexes are superior for small dimensional point clouds (3 dimensions and below). 
This advantage becomes especially clear at high number of points.
However, without sufficient computational resources, Alpha complexes were not usable for point cloud dimensions greater than 3. 
If data is more than three dimensions, then it should be dimensionally reduced by a procedure such as PCA for before using alpha complexes.

>>>>

Figure \ref{fig:fin} shows that at high point cloud sizes, GUDHI’s alpha complex outperforms Ripser. 
Theoretically, alpha complexes gain polynomial complexity as the number of points increases whereas Vietoris-Rips complexes gain exponentially \citep{roadmap}.
Specifically, alpha complexes are $O(n^{d/2})$ and Vietoris-Rips complexes are $O(2^n)$ where $n$ is the number of points on a point cloud and $d$ is the dimensions on the point cloud. 
For the conditions in our paper, Vietoris-Rips and alpha complexes both performed better than their theoretical maximums.
Vietoris-Rips complex calculations consistently had a polynomial growth for both runtime and boundary matrix size while alpha complexes had linear growth.

@@

Based on the theoretical complexity and our results, alpha complexes are superior for point clouds with 3 or fewer dimensions. 
This advantage becomes especially clear at high number of points.
However, without sufficient computational resources, Alpha complexes were not usable for point cloud dimensions greater than 3. 
If data is more than three dimensions, then it should be dimensionally reduced by a procedure such as PCA for before using alpha complexes.
